Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-21 paper/structureScene.tex
write on the number of layers and the required invariance

>>>>

The scattering transform is defined mathematically as an infinite cascade of nonlinear layers, each consisting of a wavelet transform modulus operator.
However, to achieve invariance to translation up to $T = 186\,\mathrm{ms}$, \ie of the order of the minimal duration between non-overlapping acoustic events, however, two layers of scattering transform of the audio signal $\boldsymbol{x}(t)$ suffice.
The next section describes the operations involved in temporal scattering.
